---
title: "Notes For Results"
author: "Diana Portugal"
date: "6/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Results 

The relationships that resulted included:


* peacrabs.f_1_vs_0
    + [Grey]*Peacrabs presence absence* 
* RFTM_pa1.peacrabs.f1
    + RFTM score and Peacrab presence absence
* RFTM_pa_1_vs_0
    + RFTM score presence absence
* Site.x_OY_vs_NW
    + Site OY and Site NW
* Site.x_SW_vs_NW
    + Site SW and Site NW
* RFTM_pa1.Site.xOY
    + RFTM score presence absence and Site OY
* RFTM_pa1.Site.xSW
    + RFTM score presence absence and Site SW
* peacrabs.f1.Site.xOY
    + Peacrabs presence absence and Site OY
* peacrabs.f1.Site.xSW
    + Peacrabs presence absence and Site SW



* unordered list
* item 2
    + sub-item 1
    + sub-item 2

1. ordered list
2. item 2
    + sub-item 1
    + sub-item 2 


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
